\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-02 doc/paper.tex
doc/paper.tex: reduce repetition of "straightforward"
doc/paper.tex: change "auto-generated" -> "out of the box"
Since the NUHMSSM executable is also auto-generated to some extent.

By definition, research is an endeavour to find something new.
Therefore, it can often be the case that
an auto-generated spectrum generator executable is not enough.
\fs attempts to offer a clean interface through which
one can exploit its facilities
while undergoing a minimal amount of frustration,
when he or she programs for a wide variety of studies.
In what follows,
this property shall be demonstrated by presenting a few use cases
at differing levels of complexity.

@@

To prepare the main source file \code{run_tower.cpp},
one can make a straightforward extension to
\code{run_MSSM.cpp} or \code{run_MSSMRHN.cpp}
produced in either model directory.
The shipped example reads:
\begin{numlstlisting}
#include "MSSM_MSSMRHN_spectrum_generator.hpp"

@@

% \begin{numlstlisting}
% template<>
% class MSSM_MSSMRHN_initial_guesser<Two_scale> : public Initial_guesser<Two_scale> {
% public:
%   MSSM_MSSMRHN_initial_guesser(MSSM<Two_scale>*, MSSMRHN<Two_scale>*,
%                                const MSSMRHN_input_parameters&,
%                                const QedQcd&,
%                                const MSSM_low_scale_constraint<Two_scale>&,
%                                const MSSM_susy_scale_constraint<Two_scale>&,
%                                const MSSMRHN_high_scale_constraint<Two_scale>&,
%                                const MSSM_MSSMRHN_matching<Two_scale>&);
%   virtual ~MSSM_MSSMRHN_initial_guesser();
%   virtual void guess();
%
% private:
%   MSSM   <Two_scale>* model_1;
%   MSSMRHN<Two_scale>* model_2;
%   MSSMRHN_input_parameters input_pars;
%   QedQcd oneset;
%   MSSM_low_scale_constraint<Two_scale> low_constraint;
%   MSSM_susy_scale_constraint<Two_scale> susy_constraint;
%   MSSMRHN_high_scale_constraint<Two_scale> high_constraint;
%   MSSM_MSSMRHN_matching<Two_scale> matching;
% };
% \end{numlstlisting}
The last missing piece is the initial guesser.
One can extend the already available
\code{MSSM_initial_guesser} class in a straightforward manner.
The essential task is done by the following member function:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
void MSSM_MSSMRHN_initial_guesser<Two_scale>::guess()
{
  // guess SUSY couplings in model-1 at low energy;

>>>>

By definition, research is an endeavour to find something new.
Therefore, it can often be the case that
a spectrum generator right out of the box is not enough.
\fs attempts to offer a clean interface through which
one can exploit its facilities
while undergoing a minimal amount of frustration,
when he or she programs for a wide variety of studies.
In what follows,
this property shall be demonstrated by presenting a few use cases
at differing levels of complexity.

@@

To prepare the main source file \code{run_tower.cpp},
one can extend % make a straightforward extension to
\code{run_MSSM.cpp} or \code{run_MSSMRHN.cpp}
produced in either model directory.
The shipped example reads:
\begin{numlstlisting}
#include "MSSM_MSSMRHN_spectrum_generator.hpp"

@@

% \begin{numlstlisting}
% template<>
% class MSSM_MSSMRHN_initial_guesser<Two_scale> : public Initial_guesser<Two_scale> {
% public:
%   MSSM_MSSMRHN_initial_guesser(MSSM<Two_scale>*, MSSMRHN<Two_scale>*,
%                                const MSSMRHN_input_parameters&,
%                                const QedQcd&,
%                                const MSSM_low_scale_constraint<Two_scale>&,
%                                const MSSM_susy_scale_constraint<Two_scale>&,
%                                const MSSMRHN_high_scale_constraint<Two_scale>&,
%                                const MSSM_MSSMRHN_matching<Two_scale>&);
%   virtual ~MSSM_MSSMRHN_initial_guesser();
%   virtual void guess();
%
% private:
%   MSSM   <Two_scale>* model_1;
%   MSSMRHN<Two_scale>* model_2;
%   MSSMRHN_input_parameters input_pars;
%   QedQcd oneset;
%   MSSM_low_scale_constraint<Two_scale> low_constraint;
%   MSSM_susy_scale_constraint<Two_scale> susy_constraint;
%   MSSMRHN_high_scale_constraint<Two_scale> high_constraint;
%   MSSM_MSSMRHN_matching<Two_scale> matching;
% };
% \end{numlstlisting}
The last missing piece is the initial guesser.
One can extend the already available
\code{MSSM_initial_guesser} class. % in a straightforward manner.
The essential task is done by the following member function:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
void MSSM_MSSMRHN_initial_guesser<Two_scale>::guess()
{
  // guess SUSY couplings in model-1 at low energy;
